Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
add depth discussion

As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
increases with deeper trees. The reason is twofold. First, the deeper the
tree, the larger is the conditioning. As it was observed in the comparison
between correlation and partial correlation, it screens indirect links in the
infered network. Second, the number of trees when trees are small need to be
much higher in order to correctly estimate all pairs. However, as suggested by
\cite{Gilles2014understanding}, limiting the maximal depth of trees may help
to reduce the misestimation bias in variable importance comuting, i.e.
infering the strengh of a link.

>>>>

As it can also be seen on Figure \ref{fig:curves}, the GENIE3 performance
increases with deeper trees in addition to be computionnally feasible. The
reason is twofold. First, the deeper the tree, the larger is the conditioning.
As it was observed in the comparison between correlation and partial
correlation, it screens indirect links in the infered network. Second, the
number of small trees need to be much higher than deep trees in order to
observe - and evaluate - all pairs.  However, as suggested by
\cite{louppe2014understanding}, limiting the maximal depth of trees may help
to reduce the misestimation bias in variable importance comuting, i.e.
infering the strengh of a link. Therefore a trade-off of the maximal depth may give the best of both worlds.
